Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-06 MCQMC2022ChallengesQMCSoftwareArticle.tex
SC: Fixed a few latex errors. Added a suggestion.

%\input FJHDef.tex
\newcommand{\AGSComment}[1]{{\color{red} #1}}

@@

>>>>

%\input FJHDef.tex
\newcommand{\AGSComment}[1]{{\color{red} #1}}
\newcommand{\FredComment}[1]{{\color{blue} Fred: #1}}
\newcommand{\SCComment}[1]{{\color{green} Sou-Cheng: #1}}
\newcommand{\YDComment}[1]{{\color{orange} Yuhan: #1}}
\newcommand{\JagsComment}[1]{{\color{violet} Jags: #1}}
\DeclareMathOperator{\disc}{disc}

@@

\SCComment{Somewhere in this section or Section 8, perhaps we could say that we will use QMCPy for illustration. Something like: We draw on our collective experiences as 
members of the academic community in the (Q)MC area; developers of open-source and commercial scientific software; users of (Q)MC and a wide range of scientific software as research scientists or data scientists. We highlight the insights we have gained in developing the (Q)MC scientific software packages, QMCPy~\cite{} and GAIL~\cite{}. In particular, QMCPy is not only a QMC software, but also a scientific middleware framework, which provides access to  more than X (Q)MC scientific software such as A~\cite{}, B~\cite{}, C~\cite{}.}
